\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage[]{natbib}
\bibliographystyle{plainnat}

\date{}

\begin{document}

\hypertarget{arterial-spin-labeled-mri-preprocessing-and-cerebral-blood-flow-computation}{%
\subsubsection{Arterial Spin-Labeled MRI Preprocessing and Cerebral
Blood Flow
Computation}\label{arterial-spin-labeled-mri-preprocessing-and-cerebral-blood-flow-computation}}

Arterial spin-labeled MRI images were preprocessed using \emph{ASLPrep}
0.2.7beta, which is based on \emph{Nipype} 1.6.1 \citep{nipype}.

\hypertarget{anatomical-data-preprocessing}{%
\subsubsection{Anatomical data
preprocessing}\label{anatomical-data-preprocessing}}

\emph{sMRIPrep} 0.6.1 was used to process the anatomical data. A total
of 1 T1-weighted (T1w) image was found within the input BIDS dataset.
The T1-weighted (T1w) image was corrected for intensity non-uniformity
(INU) with \texttt{N4BiasFieldCorrection} \citep{n4}, which is
distributed with \emph{ANTs} 2.3.1 \citep{ants}. \emph{sMRIPrep} uses
this T1w reference throughout the workflow. The T1w-reference was then
skull-stripped with a \emph{Nipype} implementation of the
\texttt{antsBrainExtraction.sh} workflow using OASIS30ANTs as the target
template. Brain tissue segmentation of cerebrospinal fluid (CSF),
white-matter (WM) and gray-matter (GM) was performed on the
brain-extracted T1w reference image using \emph{FSL}'s \texttt{FAST}
\citep{fsl_fast}. Nonlinear registration of the brain-extracted T1w
reference image to the brain-extracted template was accomplished using
\texttt{antsRegistration}. The following template was selected for
spatial normalization: \emph{ICBM 152 Nonlinear Asymmetrical template
version 2009c} \citep{mni152nlin2009casym},

\hypertarget{asl-data-preprocessing}{%
\subsubsection{ASL data preprocessing}\label{asl-data-preprocessing}}

For the 1 ASL run found per subject (across all tasks and sessions), the
following preprocessing was performed. First, the middle volume of the
ASL timeseries was selected as the refernce volume and brain extracted
using \emph{Nipype}'s custom brain extraction workflow. Head-motion
parameters were estimated using \emph{FSL}'s \texttt{mcflirt}
\citep{mcflirt}. Next, ASLPrep wrote head-motion parameters to the ASL
run's confound file.

Susceptibility distortion correction (SDC) was omitted. ASLPrep
co-registered the ASL reference to the T1w reference using \emph{FSL}'s
\texttt{flirt} \citep{flirt}, which implemented the boundary-based
registration cost-function \citep{bbr}. Co-registration used 6 degrees
of freedom. The quality of co-registration and normalization to template
was quantified using the Dice and Jaccard indices, the cross-correlation
with the reference image, and the overlap between the ASL and reference
images (e.g., image coverage). Several confounding timeseries were
calculated, including both framewise displacement (FD) and DVARS. FD and
DVARS are calculated using the implementations in in \emph{Nipype}
(following the definition by \citep{power_fd_dvars}) for each ASL run.
ASLPrep summarizes in-scanner motion as the mean framewise displacement
and relative root-mean square displacement.

\hypertarget{cerebral-blood-flow-computation-and-denoising}{%
\subsubsection{Cerebral blood flow computation and
denoising}\label{cerebral-blood-flow-computation-and-denoising}}

\emph{ASLPrep} was configured to calculate cerebral blood flow (CBF)
using the following methods.

The cerebral blood flow (CBF) was quantified from preprocessed ASL data
using a general kinetic model
\citep{detre_perfusion, alsop_recommended}.

Structural Correlation based Outlier Rejection (SCORE) algorithm was
applied to the CBF timeseries to discard CBF volumes with outlying
values \citep{score_dolui} before computing the mean CBF. Following
SCORE, the Structural Correlation with RobUst Bayesian (SCRUB) algorithm
was applied to the CBF maps using structural tissue probability maps to
reweight the mean CBF \citep{score_dolui, scrub_dolui}.

CBF was also computed with Bayesian Inference for Arterial Spin Labeling
(BASIL) \citep{chappell_basil}, as implemented in \emph{FSL} 6.0.3.
BASIL computes CBF using a spatial regularization of the estimated
perfusion image and additionally calculates a partial-volume corrected
CBF image \citep{chappell_pvc}. For each CBF map, the ROIs for the
following atlases were extracted: the Harvard-Oxford and the Schaefer
200 and 400-parcel resolution atlases.

The Quality evaluation index (QEI) was computed for each CBF map
\citep{cbfqc}. QEI is based on the similarity between the CBF and the
structural images, the spatial variability of the CBF image, and the
percentage of grey matter voxels containing negative CBF values.\\
All resampling in \emph{ASLPrep} uses a single interpolation step that
concatenates all transformations. Gridded (volumetric) resampling was
performed using \texttt{antsApplyTransforms}, configured with
\emph{Lanczos} interpolation to minimize the smoothing effects of other
kernels \citep{lanczos}. Many internal operations of \emph{ASLPrep} use
\emph{Nilearn} 0.8.0 \citep{nilearn}, \emph{NumPy} \citep{numpy}, and
\emph{SciPy} \citep{scipy}. For more details of the pipeline, see
\href{https://aslprep.readthedocs.io/en/latest/workflows.html}{the
\emph{ASLPrep} documentation.}.

\hypertarget{copyright-waiver}{%
\subsubsection{Copyright Waiver}\label{copyright-waiver}}

The above methods description was automatically generated by
\emph{ASLPrep} with the express intention that users should copy and
paste this text into their manuscripts unchanged. It is released under
the unchanged
\href{https://creativecommons.org/publicdomain/zero/1.0/}{CC0} license.

\hypertarget{references}{%
\subsubsection{References}\label{references}}

\bibliography{/usr/local/miniconda/lib/python3.7/site-packages/aslprep/data/boilerplate.bib}

\end{document}
